%% Dr Alun Moon
%% assignment-template.tex, generated from assignment-template.dtx
\documentclass[12pt]{article}
\usepackage[british]{babel}

\usepackage{url}
\usepackage[round]{natbib}
\usepackage{infoboxes}

\usepackage{latexsym}
\usepackage{tlatex}
\usepackage{color}
\definecolor{boxshade}{gray}{.8}
\setboolean{shading}{true}

\usepackage{enumerate,
            siunitx}

\begin{document}

\section{{Specification}}
\subsection{The Specification} 
\begin{tla}
------------------------------- MODULE bridge -------------------------------
EXTENDS Naturals, Sequences 
CONSTANT Cars, Capacity

VARIABLE bridge

Init == bridge = <<>>

Type == bridge \in Seq(Cars)

Safe == Len(bridge) \leq Capacity
--------
(* Test to see if a value is in a sequence *)
IsOnBridge(a) == \E n \in DOMAIN bridge : bridge[n] = a 

enter(c) == 
     /\ c \in Cars
     /\ \lnot IsOnBridge(c)
     /\ Len(bridge)<Capacity
     /\ bridge' = Append(bridge, c)
exit == 
    /\ Len(bridge) > 0
    /\ bridge' = Tail(bridge)
--------
Next ==
    \/ \E c \in Cars : enter(c)
    \/ exit
=============================================================================
\* Modification History
\* Last modified Fri Feb 12 20:31:31 GMT 2021 by alunm
\* Created Thu Feb 11 10:48:41 GMT 2021 by alunm
\end{tla}
\begin{tlatex}
\@x{}\moduleLeftDash\@xx{ {\MODULE} bridge}\moduleRightDash\@xx{}%
\@x{ {\EXTENDS} Naturals ,\, Sequences}%
\@x{ {\CONSTANT} Cars ,\, Capacity}%
\@pvspace{8.0pt}%
\@x{ {\VARIABLE} bridge}%
\@pvspace{8.0pt}%
\@x{ Init\@s{5.13} \.{\defeq} bridge \.{=} {\langle} {\rangle}}%
\@pvspace{8.0pt}%
\@x{ Type \.{\defeq} bridge \.{\in} Seq ( Cars )}%
\@pvspace{8.0pt}%
\@x{ Safe\@s{2.40} \.{\defeq} Len ( bridge ) \.{\leq} Capacity}%
\@x{}\midbar\@xx{}%
\@x{}%
\@y{%
  Test to see if a value is in a sequence 
}%
\@xx{}%
 \@x{ IsOnBridge ( a ) \.{\defeq} \E\, n \.{\in} {\DOMAIN} bridge \.{:} bridge
 [ n ] \.{=} a}%
\@pvspace{8.0pt}%
\@x{ enter ( c ) \.{\defeq}}%
\@x{\@s{27.54} \.{\land} c \.{\in} Cars}%
\@x{\@s{27.54} \.{\land} {\lnot} IsOnBridge ( c )}%
\@x{\@s{27.54} \.{\land} Len ( bridge ) \.{<} Capacity}%
\@x{\@s{27.54} \.{\land} bridge \.{'} \.{=} Append ( bridge ,\, c )}%
\@x{ exit \.{\defeq}}%
\@x{\@s{16.4} \.{\land} Len ( bridge ) \.{>} 0}%
\@x{\@s{16.4} \.{\land} bridge \.{'} \.{=} Tail ( bridge )}%
\@x{}\midbar\@xx{}%
\@x{ Next \.{\defeq}}%
\@x{\@s{16.4} \.{\lor} \E\, c \.{\in} Cars \.{:} enter ( c )}%
\@x{\@s{16.4} \.{\lor} exit}%
\@x{}\bottombar\@xx{}%
\@x{}%
\@y{%
  Modification History
}%
\@xx{}%
\@x{}%
\@y{%
  Last modified Fri Feb 12 20:31:31 GMT 2021 by alunm
}%
\@xx{}%
\@x{}%
\@y{%
  Created Thu Feb 11 10:48:41 GMT 2021 by alunm
}%
\@xx{}%
\end{tlatex}

\section{The Model}
\subsection{Model Overview}
\paragraph{The Behaviour specification} is an \emph{Initial predicate and
next-state relation}
\subparagraph{Initial predicate} \textit{Init}
\subparagraph{Next-state relation} \textit{Next}

\paragraph{The Model} values assigned to declared constants
\subparagraph{The set of cars in the model} $\mathit{Cars} \leftarrow 1..10$
\subparagraph{The capacity of the bridge} $\mathit{Capacity} \leftarrow 3$
\subsection{Checks and verifications}
\paragraph{Invariants} Two invariants are checked
\subparagraph{The Type Invariant} \textit{Type}
\subparagraph{The Safety Invariant} \textit{Safe}

\subsection{Results} A summary of the results
\paragraph{Statistics} a summary of the actions and number of states
found.

\begin{table}[h]
\begin{tabular}{lr}
	States found & \num{1641} \\
 Distinct states & \num{821} \\ 
\end{tabular}
\end{table}

\begin{table}[h]
\begin{tabular}{llrr}
	\textbf{Action} & Location & States Found & \textbf{Distinct states} \\
	\hline
	\textit{Init}   & Line 7 & 1 & 1 \\
	\textit{enter}   & Line 16 & 820 & 820 \\
	\textit{exit}   & Line 21 & 820 & 0 \\
\end{tabular}
\end{table}

\subsection{Discussion}
\subsubsection{Model description} 
\paragraph{The state of the system is } modelled by a sequence of cars on the
bridge.

\subparagraph{The initial conditions} are that the bridge is empty

\subparagraph{The type invariant} is that the state-variable \emph{bridge} is
a sequence of cars from the model set.

\subparagraph{The safety invariant} is that the length of the sequence is not
greater than the bridge capacity.

\paragraph{The Next relation} is that there is some car that can enter the
bridge, or that a car exits the bridge.

\subparagraph{A car can enter the bridge if } it is not already on the bridge,
and the bridge has not reached its capacity.

\subsubsection{Interpretation of results}
The specification verifies with the model, the type and safety invariants are
kept.  There isn't a set to see if the order of cars entering and leaving the
bridge matches, we can infer this is the case from the definition of
sequences.

\end{document}

\endinput
%%
%% End of file `assignment-template.tex'.
